---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# epimodelac

<!-- badges: start -->
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of `epimodelac` is to host tutorials for the workshop on "Análisis de Brotes y Modelamiento en Salud Pública". 

For more information please consult <https://epimodelac.com/>.

## Usage

Visualize this content as a webpage at <https://epiverse-trace.github.io/epimodelac/>

<!-- To build the website locally, please refer to [the contributing guidelines](CONTRIBUTING.md). -->

## Contributing

Contributions are always welcome!

See our [Contributing guide](CONTRIBUTING.md) for ways to get started.

Please adhere to this project's [Code of Conduct](CODE_OF_CONDUCT.md).

<!-- ## Support -->

<!-- Please see our [Getting help guide](/.github/SUPPORT.md) for support. -->

## License

Read the [License](LICENSE.md) of this tutorial.

## Authors

- [@Joskerus](https://github.com/Joskerus/)

```{r,eval=FALSE,echo=FALSE}
readCitationFile(file = "inst/CITATION")
```
